---
title: "classification models"
author: "Prabin Kharel"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Prepare Data for classification

```{r}
library(haven)
bank_loan_df <- read_sav("P4_bankloan_5000_clients.sav")
```

```{r}
bank_loan_df$defaulted_loan<-as.factor(bank_loan_df$defaulted_loan)
bank_loan_df$education_level<-as.factor(bank_loan_df$education_level)
```

```{r}
str(bank_loan_df)
```

###Split data into training and testing set
```{r}
library(caret)
set.seed(1234)
ind<-sample(2,nrow(bank_loan_df),replace=T,prob = c(0.7,0.3))
train_data<-bank_loan_df[ind==1,]
test_data<-bank_loan_df[ind==2,]
```

###Logistic Regression with validation

#### Training Logistic Regression Model
```{r warning=FALSE}
log_clf<-train(defaulted_loan~.,
  data=train_data,
  method="glm",
  family="binomial"
)
summary(log_clf)
```


#### Making the Prediction
```{r}
predicted_log<-predict(log_clf,newdata = test_data)

```



#### Confusion Matrix for Evaluation
```{r}
confusionMatrix(test_data$defaulted_loan, predicted_log)
```



### KNN Model with train/test validation

#### Training KNN Model
```{r}
knn_clf<-train(defaulted_loan~.,data = train_data,
               method="knn",
               preProcess = c("center", "scale"),
               tuneLength = 10
               )
```

#### Getting the Result of the Model

```{r}
knn_clf$result
```

#### Confusion Matrix for Model Evaluation 
```{r}
predicted_val_knn<-predict(knn_clf,newdata = test_data)
confusionMatrix(test_data$defaulted_loan, predicted_val_knn)
```

### Naïve Bayes classifier

#### Training the Naïve Bayes classifier
```{r}
library(e1071)
naive_clf<-naiveBayes(defaulted_loan~.,data=train_data)
summary(naive_clf)
```


####Making the Prediction in the test data
```{r}
predicted_naive<-predict(naive_clf,newdata = test_data)
```

#### Confusion Matrix for Evaluation
```{r}
confusionMatrix(predicted_naive,test_data$defaulted_loan)
```


### Support Vector Machine (SVM) Model

#### Training the Model
```{r}
svm_clf<-train(defaulted_loan~.,
               data=train_data,
               method="svmLinear"
               )
svm_clf
```
#### Making the Prediction for test data
```{r}
predicted_svm<-predict(svm_clf,newdata = test_data)
```

#### Confusion Matrix for Model Evaluation
```{r}
confusionMatrix(predicted_svm,test_data$defaulted_loan)
```

###Decision Tree 

####Trainig the Decision tree model
```{r}
dtree_clf<-train(defaulted_loan~.,
                 data = train_data,
                 method="rpart",
                 parms = list(split = "information"),
                 tuneLength=10
                 )
dtree_clf
```

#### Making the Prediction for test data
```{r}
predicted_dtree<-predict(dtree_clf,newdata = test_data)
```

####Confusion Matrix for Model Evaluation
```{r}
confusionMatrix(predicted_dtree,test_data$defaulted_loan)
```

### Artifical Neural Network (ANN) Model

#### Training the Model
```{r}
ann_clf <- train(defaulted_loan ~ ., data = train_data, 
  method = "nnet",
  preProcess = c("center","scale"), 
  maxit = 250,    # Maximum number of iterations
  tuneGrid = data.frame(size = 1, decay = 0),
  # tuneGrid = data.frame(size = 0, decay = 0),skip=TRUE, # Technically, this is log-reg
  metric = "Accuracy")
```

#### Making the Predictions for Test data
```{r}
predicted_val_ann<-predict(ann_clf,newdata = test_data)
```

#### Confusion Matrix for the Model Evaluation
```{r}
confusionMatrix(predicted_val_ann,test_data$defaulted_loan)
```